### 2016-11-04 introduction.tex
more shit

We observed evidence of this phenomenon in our experiments, and this is the motivation behind our decision to evaluate our pruning algorithms on the simple criteria of their ability to trim neurons \textit{without} any re-training. If we were to employ re-training as part of our evaluation criteria, we would arguably \textit{not} be evaluating the quality of our algorithm's pruning decisions per se but rather the ability of back-propagation trained networks to recover from faults, as per (\cite{segee1991fault} \cite{mozer1989skeletonization}). As \cite{fahlman1989cascade} discuss, the ``herd effect'' and ``moving target'' problems in back-propagation learning will simply cause the remaining units in a network to shift course and re-learn whatever error signal is either re-introduced or forgotten as a result of a network fault. So long as a network has enough critical parameters to learn the function in question, a network can likely recover with additional training.

>>>>

We observed evidence of this phenomenon in our experiments, and this is the motivation behind our decision to evaluate our pruning algorithms on the simple criteria of their ability to trim neurons \textit{without} any re-training. If we were to employ re-training as part of our evaluation criteria, we would arguably \textit{not} be evaluating the quality of our algorithm's pruning decisions per se but rather the ability of back-propagation trained networks to recover from faults, as per the results of \cite{segee1991fault},  \cite{mozer1989skeletonization}. Moreover, as \cite{fahlman1989cascade} discuss, the ``herd effect'' and ``moving target'' problems in back-propagation learning will simply cause the remaining units in a network to shift course and re-learn whatever error signal is either re-introduced or forgotten as a result of a network fault. So long as a network has enough critical parameters to learn the function in question, a network can likely recover with additional training.
